The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
little todos and refs

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (open, forest and lichen) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019].

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology.
We aggregated the 10m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100m, 250m, 500m, and 1000m. Aggregation occurred
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
for caribou during foraging <!--TODO: REF-->, while re-sampling at 500m and 1000m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017).

### Temporal scale
<!--TODO: are we missing some mention of 2017 summer and 2018 winter somewhere?-->
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (1 January)
and summer (3 August). The position of the time window was shifted by 1-48 days,
using a fixed time window length of 48 days. These new time windows were
iteratively used to partition data into two discrete seasons (winter, summer)
and generate multilayer networks.

@@

1. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?

1. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment across scales? What is
the role of memory, and by extension social and spatial cognition, as animals
navigate their environment and make decisions about where to move next?

>>>>

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (open, forest and lichen) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019]. *FIX VANDER WAL IN SPATSOC REF*

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology.
We aggregated the 10m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100m, 250m, 500m, and 1000m. Aggregation occurred
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500m and 1000m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017).

### Temporal scale
<!--TODO: are we missing some mention of 2017 summer and 2018 winter somewhere?-->
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (starting at 1 January)
and summer (starting at 3 August). The position of the time window was shifted by 1-48 days,
using a fixed time window length of 48 days. These new time windows were
iteratively used to partition data into two discrete seasons (winter, summer)
and generate multilayer networks.

@@

2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?

3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment across scales? What is
the role of memory, and by extension social and spatial cognition, as animals
navigate their environment and make decisions about where to move next?
